Peaks and valleys of prolatin-related gene expression during pigeon parental care stages

### 2019-09-07 docs/characterization_manuscript.Rmd
done with updates

```{r, fig.width= 5, echo = F, fig.cap = "MDS plots of all samples."}
ggdraw() + draw_image("../figures/limma/plotMDS-colored-1.png") 
```

>>>>

```{r, fig.width= 5, echo = F, fig.cap = "MDS plots of all samples. Needs improvement but shows that tissue is source of main variation whereas sex really only affects the gonads and treatment isn't noticable at this levels of analysis."}
ggdraw() + draw_image("../figures/limma/plotMDS-colored-1.png") 
```
